Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
finished conclusion

\section{Future work and conclusion}
\todo{Write section}

@@

Inlining in Sista
We need to add support, are we going to have a new representation to maintain and evolve \cite{SistaFastStartUp}

>>>>

\section{Future work and conclusion}

In this section we discuss two future work directions and conclude.

@@

For the past few years, an experimental adaptive optimizer (a JIT featuring advanced optimizations such as speculative inlining) has been developed on top of the Cog VM \cite{SistaFastStartUp}. The optimizer has specific rules to be able to inline primitive operations without performance loss. We need to carefully measure, in different benchmarks, the performance of the inlined string comparison primitive. We also need to discuss the maintenance cost, for example, do we need a new representation of the primitive for the optimizing JIT to inline it? The micro-benchmarks used in the paper were relevant to show the client stack to C stack switch overhead as well as baseline performance. In the optimizing JIT context, such micro-benchmarks are not really relevant anymore since the optimizing JIT usually entirely optimizes away such benchmarks and real-application performance depends on how well the primitive is inlined and specialized using information from the optimized method (typically, if one operand of the string comparison is a constant string, can the generated code benefit from this knowledge?).
